\documentclass[a4paper,12pt,reqno]{amsart}
%\usepackage{times} %,fullpage}%,backref}
\usepackage{latexsym,amscd,amssymb,url}
\pagestyle{headings}
\usepackage{xcolor, mathtools}
\PassOptionsToPackage{pdfusetitle,pagebackref,colorlinks}{hyperref}
\usepackage{bookmark}
\hypersetup{
  linkcolor={red!70!black},
  citecolor={green!70!black},
  urlcolor={teal!80!black},
	linkcolor={teal!80!black}
}
%\definecolor{dblue}{rgb}{0,0,.6}
%\usepackage[colorlinks=true, linkcolor=dblue, citecolor=dblue, filecolor = dblue, menucolor = dblue, urlcolor = dblue]{hyperref}

\textwidth=450pt 
\oddsidemargin=12pt
\evensidemargin=12pt
\renewcommand{\baselinestretch}{1.2}
\setlength{\footskip}{25pt}
%
%\setlength{\headheight}{6.15pt}
%\setlength{\headsep}{0.5cm}
%\setlength{\headheight}{6.15pt}
%\setlength{\headsep}{1.0cm}
%\usepackage[latin1]{inputenc} 	
%\usepackage[T1]{fontenc}         
%\usepackage{ae}									
%\usepackage[arrow, matrix, curve]{xy}  
\usepackage[all,cmtip]{xy}  
\usepackage{graphicx}
%\usepackage{MnSymbol} 
\usepackage{color}
\usepackage{hyperref}
\usepackage{enumerate}

	
\usepackage[T1]{fontenc}         
\usepackage{ae}									
%\usepackage[arrow, matrix, curve]{xy}  
\usepackage[all,cmtip]{xy}  
\usepackage{graphicx}
%\usepackage{MnSymbol} 
\usepackage{color}

\interfootnotelinepenalty=10000


%----------------------------------------------
% Theorem like environments
%
\newtheorem{theorem}{Theorem}[section]
\newtheorem*{theoremnocount}{Theorem}
\theoremstyle{plain}
\newtheorem*{acknowledgement}{Acknowledgement}
\newtheorem{question}[theorem]{Question}
\newtheorem{statement}{Statement}
\newtheorem{case}{Case}
\newtheorem{claim}{Claim}
\newtheorem{conclusion}{Conclusion}
\newtheorem{condition}{Condition}
\newtheorem{conjecture}[theorem]{Conjecture}
\newtheorem{corollary}[theorem]{Corollary}
\newtheorem{criterion}{Criterion}
\theoremstyle{definition}
\newtheorem{definition}[theorem]{Definition}
\newtheorem{example}[theorem]{Example}
\newtheorem{exercise}{Exercise}
\newtheorem{lemma}[theorem]{Lemma}
\newtheorem{notation}{Notation}
\newtheorem{problem}{Problem}
\newtheorem{proposition}[theorem]{Proposition}
\theoremstyle{remark}
\newtheorem{remark}[theorem]{Remark}
\newtheorem{solution}{Solution}
\newtheorem{fact}{Fact}
\newtheorem*{convention}{Convention}

\setcounter{tocdepth}{1}

%---------------------------------------------------
%newcommads
\newcommand{\delbar}{\overline{\partial}}
\newcommand{\del}{\partial}
\newcommand{\Z}{\mathbb Z}
\newcommand{\Q}{\mathbb Q}
\newcommand{\PP}{\mathbb P}
\newcommand{\Qbar}{\overline{\mathbb Q}}
\newcommand{\C}{\mathbb C}
\newcommand{\N}{\mathbb N}
\newcommand{\R}{\mathbb R}
\newcommand{\HH}{\mathbb H}
\newcommand{\CP}{\mathbb P}
\newcommand{\OO}{\mathcal O}
\newcommand{\K}{\mathcal F}
\newcommand{\D}{\operatorname{D}}
\newcommand{\sV}{\mathcal V}



\newcommand{\Card}{\operatorname{Card}}
\newcommand{\alb}{\operatorname{alb}}
\newcommand{\im}{\operatorname{im}}
\newcommand{\Td}{\operatorname{Td}}
\newcommand{\Hom}{\operatorname{Hom}}
\newcommand{\Pic}{\operatorname{Pic}}
\newcommand{\Div}{\operatorname{Div}}
\newcommand{\End}{\operatorname{End}}
\newcommand{\rk}{\operatorname{rk}}
\newcommand{\Fix}{\operatorname{Fix}}
\newcommand{\Aut}{\operatorname{Aut}}
\newcommand{\sign}{\operatorname{sign}}
\newcommand{\Sym}{\operatorname{Sym}}
\newcommand{\id}{\operatorname{id}}
\newcommand{\PGL}{\operatorname{PGL}}
\newcommand{\GL}{\operatorname{GL}}
\newcommand{\Spec}{\operatorname{Spec}}
\newcommand{\Eig}{\operatorname{Eig}}
\newcommand{\RE}{\operatorname{Re}}
\newcommand{\Gal}{\operatorname{Gal}}
\newcommand{\res}{\operatorname{res}}
\newcommand{\pr}{\operatorname{pr}}
\newcommand{\NS}{\operatorname{NS}}
\newcommand{\Sing}{\operatorname{Sing}}
\newcommand{\Alb}{\operatorname{Alb}}
\newcommand{\PD}{\operatorname{PD}}
\newcommand{\SING}{\operatorname{Sing}}
\newcommand{\TD}{\operatorname{TD}}
\newcommand{\T}{\mathcal V}
\newcommand{\Bir}{\operatorname{Bir}}
\newcommand{\Amp}{\operatorname{Amp}}
\newcommand{\codim}{\operatorname{codim}}
\newcommand{\rank}{\operatorname{rank}}
\newcommand{\Nef}{\operatorname{Nef}}
\newcommand{\NE}{\operatorname{NE}}
\newcommand{\None}{\operatorname{N}_1}
\newcommand{\Ext}{\operatorname{Ext}}
\newcommand{\can}{\operatorname{can}}
\newcommand{\var}{\operatorname{var}}
\newcommand{\rat}{\operatorname{rat}}
\newcommand{\Per}{\operatorname{Per}}
\newcommand{\Br}{\operatorname{Br}}
\newcommand{\Gr}{\operatorname{Gr}}
\newcommand{\CH}{\operatorname{CH}}
\newcommand{\supp}{\operatorname{supp}}
\newcommand{\tor}{\operatorname{tors}} 
\newcommand{\red}{\operatorname{red}} 
\newcommand{\Proj}{\operatorname{Proj}} 
\newcommand{\sing}{\operatorname{sing}} 
\newcommand{\discr}{\operatorname{discr}} 
\newcommand{\cl}{\operatorname{cl}} 
\newcommand{\ram}{\operatorname{ram}} 
\newcommand{\Frac}{\operatorname{Frac}}
%\newcommand{\char}{\operatorname{char}}
\newcommand{\Val}{\operatorname{Val}}
\newcommand{\F}{\mathbb F}
\newcommand{\Char}{\operatorname{Char}}
\newcommand{\coker}{\operatorname{coker}}
\newcommand{\Loc}{\operatorname{Loc}}
\newcommand{\length}{\operatorname{length}}
\newcommand{\Jac}{\operatorname{Jac}}

 
\newcommand{\dashedlongrightarrow}{\xymatrix@1@=15pt{\ar@{-->}[r]&}}
\renewcommand{\longrightarrow}{\xymatrix@1@=15pt{\ar[r]&}}
\renewcommand{\mapsto}{\xymatrix@1@=15pt{\ar@{|->}[r]&}}
\renewcommand{\twoheadrightarrow}{\xymatrix@1@=15pt{\ar@{->>}[r]&}}
\newcommand{\hooklongrightarrow}{\xymatrix@1@=15pt{\ar@{^(->}[r]&}}
\newcommand{\congpf}{\xymatrix@1@=15pt{\ar[r]^-\sim&}}
\renewcommand{\cong}{\simeq}
%--------------------------------------------------------


%-----------
%-----------Yagna's typsets--------
\usepackage{tikz-cd}
\usepackage{enumitem}

\PassOptionsToPackage{pdfusetitle,pagebackref,colorlinks}{hyperref}
\usepackage{bookmark}
\hypersetup{
  linkcolor={red!70!black},
  citecolor={green!70!black},
  urlcolor={blue!80!black}
}
\newtheorem{alphtheorem}{Theorem}
\renewcommand{\thealphtheorem}{\Alph{alphtheorem}}

%Mathcal Letters =====================
\newcommand{\sA}{\mathcal{A}}
\newcommand{\sB}{\mathcal{B}}
\newcommand{\sD}{\mathcal{D}}
\newcommand{\sF}{\mathcal{F}}
\newcommand{\sG}{\mathcal{G}}
\newcommand{\sH}{\mathcal{H}}
\newcommand{\sK}{\mathcal{K}}
\newcommand{\sL}{\mathcal{L}}
\newcommand{\sM}{\mathcal{M}}
\newcommand{\sN}{\mathcal{N}}
\newcommand{\sO}{\mathcal{O}}
\newcommand{\sP}{\mathcal{P}}
\newcommand{\sQ}{\mathcal{Q}}
\newcommand{\sT}{\mathcal{T}}
\newcommand{\sZ}{\mathcal{Z}}

%mathbb Letters======
\newcommand{\bbA}{\mathbb{A}}
\newcommand{\bbB}{\mathbb{B}}
\newcommand{\bbC}{\mathbb{C}}
\newcommand{\bbG}{\mathbb{G}}
\newcommand{\bbH}{\mathbb{H}}
\newcommand{\bbK}{\mathbb{K}}
\newcommand{\bbL}{\mathbb{L}}
\newcommand{\bbM}{\mathbb{M}}
\newcommand{\bbN}{\mathbb{N}}
\newcommand{\bbP}{\mathbb{P}}
\newcommand{\bbQ}{\mathbb{Q}}
\newcommand{\bbR}{\mathbb{R}}
\newcommand{\bbV}{\mathbb{V}}
\newcommand{\bbZ}{\mathbb{Z}}



%Script Letters ======================
\newcommand{\frf}{\mathfrak{f}}
\newcommand{\frM}{\mathfrak{M}}

\newcommand{\scrL}{\mathscr{L}}
\newcommand{\crI}{\mathscr{I}}
\newcommand{\scrK}{\mathscr{K}}
\newcommand{\scrB}{\mathscr{B}}
\newcommand{\scrC}{\mathscr{C}}
\newcommand{\scrD}{\mathscr{D}}
\newcommand{\scrE}{\mathscr{E}}
\newcommand{\scrI}{\mathscr{I}}
\newcommand{\scrQ}{\mathscr{Q}}
\newcommand{\scrR}{\mathscr{R}}
\newcommand{\scrX}{\mathscr{X}}
\newcommand{\scrY}{\mathscr{Y}}
\newcommand{\scrF}{\mathscr{F}}
\newcommand{\Dred}{\lceil D\rceil}

%Arrow Style =========================
\newcommand{\into}{\hookrightarrow}
\newcommand{\onto}{\rightarrow\hspace*{-.14in}\rightarrow}

%Math Operators ======================



\DeclareMathOperator{\alg}{alg}
\DeclareMathOperator{\BM}{BM}
\DeclareMathOperator{\Bs}{Bs}
\DeclareMathOperator{\Bsp}{\mathbf{B}_+}
\DeclareMathOperator{\SB}{\mathbf{B}}

\DeclareMathOperator{\coh}{coh}
\DeclareMathOperator{\Coker}{Coker}
 \renewcommand{\div}{\text{div}}

\DeclareMathOperator{\DR}{DR}
\DeclareMathOperator{\discrep}{discrep}
\DeclareMathOperator{\exc}{exc}

\DeclareMathOperator{\free}{free}


\DeclareMathOperator{\HHom}{\mathcal{H}\!\mathit{om}}
\DeclareMathOperator{\image}{Im}


\DeclareMathOperator{\Ind}{Ind}
\DeclareMathOperator{\Ker}{Ker}
\DeclareMathOperator{\Lie}{Lie}
\DeclareMathOperator{\op}{op}


\DeclareMathOperator{\qcoh}{qcoh}

\DeclareMathOperator{\reg}{reg}

\DeclareMathOperator{\RHHom}{\mathbf{R}\mathcal{H}\!\mathit{om}}


\DeclareMathOperator{\Spf}{Spf}
\DeclareMathOperator{\Supp}{Supp}
\DeclareMathOperator{\tors}{tors}
\DeclareMathOperator{\torsion}{torsion}
\DeclareMathOperator{\Var}{Var}
%\DeclareMathOperator{\Sym}{Sym}


\newcommand{\Ab}{\mathbf{Ab}}
\newcommand{\Aff}{\mathbf{Aff}}
\newcommand{\tB}{\tilde{B}}
\newcommand{\et}{{\acute{e}t}}

\newcommand{\Sets}{\mathbf{Sets}}
\newcommand{\cX}{\bar{X}}
\newcommand{\cP}{\bar{P}}
\newcommand{\cV}{\bar{V}}
\newcommand{\cW}{\bar{W}}
\newcommand{\sorry}[1]{\textcolor{red}{#1}}
\newcommand{\dual}[1]{\sD^{\Omega}_{M^{#1}}}


%----------------



\begin{document}  
\title[On linearity of holomorphic 1-forms with zeros]{On linearity of holomorphic 1-forms with zeros} 

\author{Yajnaseni Dutta}

%\address{}
%\email{}

\author{Feng Hao}

%\address{}
%\email{}

\author{Yongqiang Liu}

%\date{\today}
%\date{October 10, 2017; 
%\copyright{\ Stefan Schreieder 2017}}
%\subjclass[2010]{primary 14E08, 14M20; secondary 14J35, 14D06} 
%
% 14J45 Fano varieties
% 14J10 Families, moduli, classification: algebraic theory
% 	14J35   	$4$-folds
% 14M20   	Rational and unirational varieties
% 	14M22   	Rationally connected varieties
% 14D06   	Fibrations, degenerations
%  	14E08   	Rationality questions

%\keywords{rationality problem, stable rationality, decomposition of the diagonal, unramified cohomology, Brauer group, L\"uroth problem.} 



\begin{abstract} 
The goal of this article is two-fold, first we 
\end{abstract}

\maketitle

\section{Introduction}\label{intro}
\textcolor{blue!70!white}{1. Need to be consistent with projective vs Kaehler, fibered by subabelian variety vs.\ fibered by subtori etc.
2. Theorem 2.4 $R^i(X)$ are a-priori not $\bbC$-sub-hodge structures. They are subspaces of $h^{1,0}$, perhaps we mean $R^i(X)+\overline{R^i(X)}?$}

In this article we study the set of global holomorphic 1-forms  on smooth projective varieties that admit zeros. Interestingly, it has been
indicated by plethora of results (\cite{GL87, HK05, LZ05,
SS19, HS19, PS14} to name just a few) that a lot of the geometry
and topology of the variety depends on vanishing of such forms.
We first state our result in this direction and then put it in the context of 
the existing vast literature.
\begin{alphtheorem}\label{thm:smooth}
Let $f:X\to A$ be a morphism from a smooth projective variety to a simple abelian variety $A$. Then $f$ is smooth if and only if there is a global holomorphic 1-form $\omega	$ on $A$ such that $f^*\omega$ is nowhere vanishing. 
\end{alphtheorem}
In fact we prove a bit more; When $A$ is not necessarily simple
existence of a non-vanishing global holomorphic 1-form
is equivalent to certain restrictions on the so called \emph{higher discriminants} (see \ref{def:higherdiscriminants}) of the morphism $f$ in the sense
of Migliorini and Shende \cite{MiSh18}.
See Theorem \ref{thm:nonvanishing} for more details.
\begin{remark}[Previous results]
\begin{enumerate}
\item \label{item:ps} When $X$ is of general type, it was conjectured in
	\cite{HK05, LZ05} and was proved
	by Popa and Schnell \cite{PS14} every global holomorphic 1-		
	form vanishes on $X$. 
\item \label{item:hk} On the opposite extreme for any $A$, not necessarily simple when $f$ is singular along a divisor of general
		type in $A$, Hacon and Kov\'acs \cite[Proposition 3.5.]{HK05} show that
		$f^*\omega$ always admits zero.
\item The more general version of Theorem \ref{thm:smooth}
recovers both Item (\ref{item:ps}) (see Corollary \ref{cor:ps})
and Item (\ref{item:hk}) (see Corollary \ref{cor:hk}).
%\item A special case of a result of 
%Schreider \cite[Corollary 1.5]{SS19} shows for any $A$, not necessarily simple when $X$
%admits a nowhere vanishing holomorphic 1-form of the form
%$f^*\omega$, then $f(X)$ is fibered by tori. In 
%Theorem \ref{thm:nonvanishing} we show more generally that 
%existence of non-vanishing forms is in fact equivalent to existence of a higher discriminant $Z\subseteq f(X)$ fibered by tori. 
\end{enumerate}
\end{remark}


In a different direction we deal with the question
of linearity of the set of vanishing 1-forms. This is
inspired by the work of  \cite{CL73}, Carrell and Lieberman, who show that for a smooth complex projective variety $X$, the set of holomorphic tangent vector fields with zeros is a subvector space of $H^0(X, T_X)$. On the
other hand its incarnation for 1-form is far from complete.
It is known due to the generic vanishing theory
%theory of cohomology jumploci 
that only a piece of the set of all 1-forms admitting zeros, namely \emph{the resonant 1-forms} (see Definition \ref{def:resonance} below) 
form a finite union of subvector spaces inside $H^0(X, \Omega_X^1)$ \cite[Theorem 4.2]{Sim93} (see also \cite{DiPa13} from where
we borrow the terminology). 
Henceforth we call finite unions of subvector spaces as \emph{linear subvarieties}.
In this article we complete the picture. To this end we need the 
following notations.
Let $X$ be a smooth complex projective variety of $\dim X=n$. The zero set of a global holomorphic 1-form $\omega$
is given by 
\[Z(\omega) \coloneqq \{x\in X| \omega(T_xX) = 0\}\]
where $T_xX$ is the holomorphic tangent space of $X$ at $x$. 
We further denote by 
\[V^i(X):=\{ \omega\in H^0(X, \Omega_X^1) |\ \codim Z(\omega)\leq i\},\] when $i=n$ we simply use the notation $V(X)$.
%:=V^n(X)=\{\omega\in H^0(X, \Omega^1_{X}) | \ Z(\omega)\not =\emptyset\},$$  
Furthermore, for the morphism $f:X\to A$ from $X$ to an abelian variety $A$, we denote
\[V^i(f):=\{ \omega\in f^*H^0(A, \Omega_A^1) |\ \codim Z(\omega)\leq i\},\]
As before when $i=n$ we use the notation $V(f)$. Notice that by Chevalley's upper-semicontinuity theorem, $V^i(X)$ and $V^i(f)$ 
\sorry{citation?} are all algebraic sets.
%:=V^n(f)=\{\omega\in f^*H^0(A, \Omega_A^1) | \ Z(\omega)\not =\emptyset\},$$

%and  the holomorphic resonance varieties $$R_h^i(X):=\{\omega\in H^0(X, \Omega_X^1) | \ \dim H^i(H^*(X, \C), \wedge \omega)\not=0\}.$$ Mainly we will study the linearity of $V(X)$ or $V(f)$, i.e., the following problem.

%For 1-forms, 
%by cohomology jump loci theory, we know that the set $R^i_h(X)$ of holomorphic resonant 1-forms (see the following notation) form linear subvarieties. 
\begin{alphtheorem}\label{main1}
Let $f: X\to A$ be a morphism from a smooth complex projective variety $X$ to an abelian variety $A$. Then 
$V(f)$ is a linear subvariety of $H^0(X, \Omega_X^1)$. In particular, $V(X)$ is a linear subvariety. Moreover, each irreducible components of $V(f)$ are $\Q$-sub Hodge structures of $H^0(X, \Omega_X^1)$. In particular, $V(f)$ and $V(X)$ are defined over $\Q$.

%(2) If the discriminant locus of $f$ is not fibred by tori or of dimension 0, then $V(f)=f^*H^0(A, \Omega_A^1)$, i.e., every holomorphic 1-forms pullback from $A$ via $f$ has zeros.
\end{alphtheorem}
\begin{remark}
\begin{enumerate}
	\item When $X$ is of general type, the 
	result of Popa and Schnell (see \ref{cor:ps}) 
	it follows that $V(X) = H^0(X,\Omega_X^1)$ which is of course
	linear. 
	\item  When $\dim X\leq 3$ an immediate corollary of the main theorems in \cite{SS19} and \cite{HS19} is that $V(X)$ is linear.
	\item \label{item:resonance} As we have already mentioned, the \emph{$i$-th holomorphic resonance varieties} $R^i_h(X)$ for
	all $i$ are 
	known to be linear (see, e.g., \cite{DiPa13}). 
	%These are, roughly speaking, the ``topological parts'' $R_h^i(X)$ of $V(X)$.
	%More precisely they are defined as follows
	%\[R_h^i(X):=\{\omega\in H^0(X, \Omega_X^1)|\ H^i(H^*(X, \mathbb{C}), \wedge \omega)\not= 0\}\subseteq V(X).\]
%We define the \emph{holomorphic resonance varieties} to be the union $$R_h(X):=\bigcup_{i} R_h^i(X).$$ 
%Our result fill in the fact that Note that
	%when
	If $R_h \coloneqq \bigcup_{i} R_h^	i(X)= V(X)$, our theorem is a direct consequence of
	this linearity. This 
	for instance is the case when $\chi(X)\not=0$ (see Corollary \ref{ECNT}). 
\end{enumerate}

\end{remark}

To put our results in the appropriate context of the linearity results from generic vanishing package developed
in \cite{Ara92, GL87, Sim93b}
we remark that a 1-form $\omega$ does \emph{not} satisfy this resonance property if and only if its associated local
system $\bbL_\omega$ does not
admit cohomologies in any degree (see \cite[Theorem 3]{Ara92} for a proof). Therefore, these forms are precisely the ones that do not fall in the
realm of the generic vanishing theory. 

We also want to emphasize that the equality $R_h(X) = V(X)$ in Item (\ref{item:resonance}) may not always be true. An example of Debarre, Jiang and Lahoz 
\cite[Example 1.11]{DJL17} shows that the
there exists a bi-elliptic surface $S$ admitting a 1-form 
$\omega$ for which $(H^*(X, \mathbb{C}), \wedge \omega)$
is exact, yet $\omega$ admits zeros on $S$. 

More generally we expect the following to be true.
\begin{conjecture} \label{linear-vi}
Let $f: X\to A$ be a morphism from a smooth complex projective variety $X$ to an abelian variety $A$. Then $V^i(f)$ are linear subvarieties of $H^0(X, \Omega_X^1)$, i.e., $V^i(X)$ is a finite union of linear subspaces of $H^0(X, \Omega_X^1)$ for each nonnegative integer $i$. In particular $V^i(X)$ are linear.
\end{conjecture}

To this end, first using a result of Spurr \cite{Sp88}, we directly get $V^1(X)$ is linear.

\begin{alphtheorem}
Let $f: X\to A$ be a morphism from a smooth complex projective variety $X$ to an abelian variety $A$. Then $V^1(f)$ is linear. In particular, $V^1(X)$ is linear.
\end{alphtheorem}


 %What's more, we show that $V^1(f)$ consists the resonant holomorphic 1-forms vanishing along a divisor and ``negative'' 1-forms (holomorphic 1-forms, which is not  necessarily resonant, but vanishes along a rigid divisor). Also, in this article, 
We also generalize a result of Spurr \cite{Sp88} to quasi-projective varieties. 

\begin{alphtheorem} \label{main3}
Let $(X, D)$ be a pair with $X$ a complex smooth projective variety and $D$ a simple normal crossing divisor of $X$. Let $H$ be a very ample divisor on $X$. If $(X, D)$ carries a holomorphic log 1-form $0\not=\omega\in H^0(X, \Omega_X^1(\log D))$  which pullbacks to zero on an effective divisor $E$ with $E^2\cdot H^{n-2}\geq0$, then there is a morphism $f: X-D\to C$ to a smooth quasi-projective curve $C=\bar{C}-B$ (where $\bar{C}$ is the completion of $C$ and $B$ can be empty) with 

(1)  $\omega=f^*\eta$ for some $\eta\in H^0(X, \Omega_{\bar{C}}^1(\log B))$.

(2) $E$ is contained in the fiber of $f$ and $E^2\cdot H^{n-2}=0$.
\end{alphtheorem}

As a corollary we prove the linearity of the set of logarithmic holomorphic 1-forms admitting codimension one zeros.

\begin{corollary}
Let $(X, D)$ be a pair with $X$ a complex smooth projective variety and $D$ a simple normal crossing divisor of $X$. Then the set $$ V^1(X,D):=\{ w \in W(U) \mid \codim_X Z(w) \leq i \}$$ is linear.
\end{corollary}

We show that $V^1(X,D)$ consists of resonant holomorphic logarithmic 1-forms vanishing along a divisor, holomorphic logarthmic 1-forms vanishing along a rigid divisor, and holomorphic logarithmic 1-forms vanishing along some components of the boundary divisor $D$.




 
\subsection{Comments about the proof}
Much like in \cite{PS14}, for a morphism $f: X\to A$ our idea is to use a description of the set of global holomorphic 1-forms
on $X$ admitting zeros
in terms of the corresponding incidence set
\[\{(x,f^*\omega)\in X\times H^0(A,\Omega_A^1)| f^*\omega(T_xX) = 0\} \subset f^*T^*A.\] More
precisely,  we consider the following diagram 
\begin{center}
\begin{tikzcd}
	X\times f^*H^0(A, \Omega_A^1) \ar[r, "df"] \ar[d, "\tilde{f}"] & T^*X\\
	A\times H^0(A, \Omega_A^1)\simeq T^*A\dar["\pr_2"]\\
	H^0(A, \Omega_A^1)
\end{tikzcd}
\end{center}
 where $T^*X$ denotes the $2n$ dimensional 
cotangent bundle of $X$, $df$ is the usual differential, and $\tilde{f} = pr_2\circ \tilde{f}$ is the natural projection. Note that
$V(f) \simeq \tilde{f}(df^{-1}(0))$. 
The main new ingredient in the proof of
Theorem \ref{thm:smooth} and \ref{main1} is
a result of Migliorini and Shende \cite[Theorem C]{MiSh18} which ensures that $(f\times\id)(df^{-1}(0))$
is a finite union of closures of conormal bundles
$T^*_ZX$ along various subvarieties of $Z\subset A$.
Then the linearity follows from the following proposition
\begin{proposition}[=Proposition \ref{van-nonsimple}]
Let $A$ be an abelian variety and $X$ be a proper subvariety of $A$. Then the following are equivalent
\begin{enumerate}
	\item $X$ is not fibred by tori or of dimension 0. 
	\item Any holomorphic 1-form $\omega\in H^0(A, \Omega_A^1)$ restricted to $X^{\reg}$, i.e.\ $\omega|_{X_{\textnormal{reg}}}$ admits zeros on the smooth locus $X_{\textnormal{reg}}$.
\end{enumerate}
\end{proposition}
When $A$ is a
simple abelian variety this proposition says that any 1-form restricted to $X$ admits zeros on the regular locus of $X$. A proof of this statement seems to be abundantly found in the literature
see for instance \cite[Proposition 3.1]{HK05}
or \cite[Proposition 5.12]{LMW20}. In general, this result seem to be expected however we could not find a proof in the existing literature. 
Therefore we provide a complete proof (see \ref{proof:van-nonsimple}).

\sorry{words about the proof of second part}


%In fact Theorem\ref{main1} (2) implies  that for a variety of general type $X$, every holomorphic 1-form over $X$ admits zeros. This is proved in \cite{PS14}. Also, Theorem \ref{main1} (2) implies \cite[Proposition 3.4]{HK05}, which dealt with the codimension one case. As a corollary of our main theorem we have






\subsection*{Notation}

































\subsection*{Acknowledgement} 

Stefan, Jiang, Kovacs, Nero, Sabbah

\section{Preliminaries pertaining to 1-forms}

\subsection{1-forms on smooth projective varieties}

In this subsection we establish terminologies and notations that will enable us to talk about them where relevant. Unless otherwise
specified by 1-forms we will mean global holomorphic 1-forms on a smooth complex projective variety $X$.

\begin{definition}[Zero scheme of 1-forms]\label{def:zeroscheme}
For $\omega\in H^0(X, \Omega_X^1)$, the \emph{zero set} $Z(\omega)$ of $\omega$ is the algebraic set of closed point $x$ in $X$, such that $\omega(v)=0$
for all tangent vectors $v\in T_xX$ at $x$. 

The \emph{zero scheme} of $\omega$ is the closed subscheme $\sZ(\omega)$ defined by the ideal sheaf $\mathcal{I}_{\omega}$ given by the image of the morphism 
\[\mathcal{T}_X\overset{\langle\omega, \cdot\rangle}{\longrightarrow} \mathcal{O}_X.\] 
Here $\mathcal{T}_X$ is the tangent sheaf of $X$ and $\langle\omega, \cdot\rangle$ denotes the pairing of tangent field with 
the 1-form $\omega$.
\end{definition}

Recall from \S \ref{intro} that \[V(X):=\{ \omega\in H^0(X, \Omega_X^1) |\ Z(\omega)\neq \emptyset\}.\]

\begin{definition}[Resonant and (universally) nonresonant forms]\label{def:resonance}
We call a 1-form $\omega\in V(X)$ \emph{(non)resonant} if the complex 
\[(H^{\bullet}(X,\bbC), \wedge\omega)\coloneqq [\ldots\to H^{i-1}(X,\C)\overset{\wedge\omega}{\longrightarrow}H^{i}(X,\C)\overset{\wedge\omega}{\longrightarrow}H^{i+1}(X,\C)\to\ldots]\]
 is (exact) not exact. 

Moreover a 1-form $\omega\in V(X)$ is called \emph{universally nonresonant} if the complex
\newline $(H^{\bullet}(X',\bbC), \wedge\tau^*\omega)$
%\[\ldots\to H^{i-1}(X',\C)\overset{\wedge\tau^*\omega}{\longrightarrow}H^{i}(X',\C)\overset{\wedge\tau^*\omega}{\longrightarrow}H^{i+1}(X',\C)\to\ldots\]
 is exact for any \'etale over $\tau\colon X'\to X$. 

We will refer to the sequence $(H^{\bullet}(X,\bbC), \wedge\omega)$ above as the \emph{resonance sequence}.
%Also, we call a holomorphic 1-form to be a resonant 1-form if it is not a nonresonant 1-form and has zeros.
\end{definition}

\begin{remark}
\begin{enumerate}
	%\item  For any 1-form $\omega$ for which the resonance sequence $(H^{\bullet}(X,\bbC), \wedge\omega)$ is not exact, it must be the case that $\omega\in V(X)$. This is a consequence of the generic vanishing package. Since in what follows we do not use this theory much, we only 
	%outline an argument here with relevant references. Assuming the contrary, we have that
 %the Koszul complex (see e.g.\ \cite[B.2 Complexes]{Laz04a} associated to the global section $\omega$ 
	%\[K^{\bullet}\coloneqq [\sO_X\xrightarrow{\wedge\omega}\Omega_X^1\xrightarrow{\wedge\omega}\cdots\xrightarrow{\wedge\omega}\Omega_X^{n-1}\xrightarrow{\wedge\omega} \omega_X]\]
	%must be exact. Then from spectral sequence $H^p(X, \sH^q(K^{\bullet})) \Rightarrow H^{p+q}(X, \bbL_{\omega})$ with $\bbL_{\omega}$
	%denoting the local system associated to $\omega$ (see e.g.\ \cite[\S 2.2]{SS19} for a definition) we obtain
	%$H^i(X, \bbL_{\omega}) = 0$ for all $i$. Then the exactness of the resonance sequence follows from Hodge decomposition, together
	%with \cite[Theorem 3]{Ara92}. 
	%\item  (Universally) nonresonant  holomorphic 1-forms were first studied in \cite{SS19}.

\item In general by \cite[Proposition 3.4]{GL87}, if a holomorphic $\omega$ has zero scheme of codimension $\geq k$, then the complex $$\ldots\to H^{i}(X,\C)\overset{\wedge\omega}{\rightarrow}H^{i}(X,\C)\overset{\wedge\omega}{\rightarrow}H^{i}(X,\C)\to\ldots$$ is exact whenever $i<k.$ 
In particular, $(H^{\bullet}(X,\bbC), \wedge\omega)$ is exact whenever $Z(\omega) = \emptyset$. 

 
\item As mentioned in the introduction, an example of \cite{DJL17} shows that
%\cite[1.6]{SS19}, 
nonresonant holomorphic 1-form exists for bielliptic surfaces with multiple fibers. 
\end{enumerate}
\end{remark}


As we have noted in the \S \ref{intro} that the set resonant 1-forms $R_h$ is linear as a consequence of the generic vanishing theory. Since we will not go in that
direction we refer the readers to the classical literature \ref{Ara92, GL87, Sim93b}. However, we do use the following result describing the components of
$R_h$ as $\bbQ$-Hodge substructures of $H^1(X, \bbC)$. For $i=1$, this is due to Dimca, Papadima, Suciu \sorry{add reference}. For higher $i$, this is due to Dimca and Papadima:
 {\color{red} (Provide references as much as we can)}. {\color{red} (Due to Voisin?)}\textcolor{teal}{I think the result of voisin is this Deligne's lemma about rationality of Hodge substrctures. DiPa use it.} 

\begin{theorem}{\cite[Theorem C, Corollary 1.7]{DiPa13}}\label{thm: resonant}
Let $X$ be a compact K\"ahler manifold. Each irreducible component of resonance varieties $R^i(X)$ is a linear subspace of $H^1(X, \C)$ defined over $\Q$, i.e., $$R^i(X)=(R^i(X)\cap H^1(X, \Q))\otimes\C.$$ Also,  each irreducible component of $R^i(X)$ carries $\Q$-Hodge substructures of $H^1(X, \C)$.
\end{theorem} 

The above result becomes particularly simple in the following case.
\begin{corollary}
Let $f:X\to A$ be a morphism from smooth projective variety $X$ to a simple abelian  variety $A$. Then $R^i(X)\cap f^*H^0(A, \Omega_A^1)$ is $f^*H^0(A, \Omega_A^1)$ or $0$.
\end{corollary}

\begin{proof}
Since polarised Hodge structures of weight 1 naturally arise as a Hodge structure of abelian varieties, $f^*H(A, \bbC)$ must induce an irreducible polarised Hodge structure on $X$. Therefore $R^i(X)\cap f^*H(A, \Omega_A^1)$ is a $\Q$-Hodge substructure of $H^1(X, \C)$ of the simple Hodge structure $f^*H(A, \Omega_A^1)$.
\end{proof}




%Not too much information is known for nonresonant 1-forms. T
Since we are specifically interested in the nonresonant 1-forms, we collect here some of the results known about them. The following theorem is due to Schreieder \cite{SS19}, which studies some properties of zeros of nonresonant 1-forms and the albanese maps of varieties admitting nonresonant 1-forms.

\begin{theorem} \label{thm:stefan}
Let $X$ be a compact connected K\"ahler manifold with a holomorphic one-form $\omega$ such that the 
resonance complex $(H^{\bullet}(X, \C), \wedge\omega)$ given by cup product with $\omega$ is exact. Then
the zero scheme $\sZ(\omega)$ of $\omega\in H^0(X,\Omega_X^1)$ has the following properties.

(1) For any reduced irreducible component $Z \subset \sZ(\omega)$ with $d=\dim \sZ(\omega)$, $$H^d(Z, \omega_X|_Z)=0.$$
In particular, $\omega$ does not have any isolated zero.

(2) If $f : X \to A$ is a holomorphic map to a complex torus $A$ such that $\omega \in f^*H^0(A, \Omega^1_A)$,
then $f(X)\subset A$ is fibred by tori.
\end{theorem}



\subsection{1-forms on subvarieties of abelian varieties}

Let $X\subset A$ be an irreducible proper subvariety of an abelian variety. In this section we show that whether or not a 1-form $\omega\in H^0(A,\Omega_A^1)$
restricted to $X$ admits zeros on $X^{\reg}$ is determined by one of the most fundamental
 structural properties of subvarieties of abelian varieties;
 namely, whether or not
$X$ is of general type. By a result of Ueno \cite[10.9]{Uen75} this is equivalent to $X$ being not fibered by any subabelian varieties of $A$. 
When $X$ is smooth 
this seems to be a classical fact that whenever the normal bundle of $X$ is ample all $\omega|_X$ admits finitely many zeros on $X$
(see e.g.\ \cite[Lemma 3.1]{Deb}). This was generalised to subvarieties of simple abelian varieties by 
Hacon and Kov\'acs \cite[Proposition 3.1]{HK05}. A special case of more recent result of Popa and \cite{PS14} suggests that this is true whenever $X$ is smooth and
$\omega_X$ is big,
i.e.\ $X$ is of general type. Although perhaps well-known to experts, we could not find any appropriate sources in literature. Nonetheless, our proof is inspired
by their original argument in\cite[Proposition 3.1]{HK05} and the proof of \cite[Lemma 3.1]{Deb} in Debarre's expository article

\begin{proposition}\label{van-nonsimple}
Let $A$ be an abelian variety and $X$ be an irreducible proper subvariety of $A$. Then the following are equivalent

(1) $X$ is not fibred by tori or of dimension 0. 

(2) For general holomorphic 1-forms $\omega\in H^0(A, \Omega_A^1)$, the restricted holomorphic 1-form $\omega|_{X_{\textnormal{reg}}}$ admit zeros at finitely many points on the smooth locus $X_{\textnormal{reg}}$.
\end{proposition}

\begin{proof}\label{proof:van-nonsimple} (2)$\Rightarrow$ (1): Suppose $X$ is fibred by tori and $\dim X>0$, i.e.\ there exists a subabelian variety $B\subset A$ such that the fibres of the composition 

$X\into A \onto A/B$ are $B$. Taking an \'etale cover $\tau: A'\to A$, we assume $A'=B\times C$ and $X':=\tau^{-1}(X)=B\times Y\subset A'$. Then the 1-forms coming from $B$ do not vanish on smooth locus of $X'$, hence also do not on the smooth locus of $X$. 

(1)$\Rightarrow$(2): Denote $d=\dim X$, $g=\dim A$. If $d=0$ it is trivial, so we assume $d>0$. Denoting by $N$ the
vector bundle on $X^{\reg}$ given by $N_{X/A}|_{X^{\reg}}$ where $N_{X/A}$ is the normal sheaf of associated to the immersion
 \cite[\href{https://stacks.math.columbia.edu/tag/01R1}{Tag 01R1}]{stacks-project}. Associated to \[T_A|_{X^{\reg}}\onto N,\]
we obtain the following chain of maps
\[\varphi\coloneqq (\bbP(N) \to 	X^{\reg}\times \bbP(T_0{A}) \to \bbP(T_0A)=\bbP^{g-1})\]
where for a vector bundle $E$ on $X^{\reg}$ we use the notation $\bbP(E) \coloneqq \Proj_{X^{\reg}})(\Sym^d(E^{\vee}))$.
Denote by $p\colon \bbP(N)\to X^{\reg}$ the bundle map. Given
a point $s\in \bbP^g$, by construction we may associate a hyperplane $H_s\subset T_{A,0}$. Then
\begin{equation}
p\colon \varphi^{-1}(s) \overset{p}{\xrightarrow{\sim}}  \{x\in X^{\reg}| T_xX^{\reg} \subset H_s\}.
\label{eq:van-nonsimple}
\end{equation}
Denote by $S\coloneqq \varphi(\bbP(N))$ the image. If $\dim S<g$, for all $s\in S$, a general
 fibre $Z_s \coloneqq \varphi^{-1}(s)$
must have dimension $g - 1 - \dim S$. Let $A_0$ denote the abelian variety spanned by $Z_s$, then $\dim A_0 > g- 1 - \dim S$. Indeed,
our assumption implies that $Z_s$ cannot itself be an abelian variety. Since for a general $s\in S$, $H_s \supset T_xA_0$
for all $x\in p(\varphi^{-1}(s))$ by \eqref{eq:van-nonsimple}. Normalising $x$ to $0$, we obtain that $T_0A_0$
is cut out by $\dim S$ many hyperplanes in $T_0A$. But $\dim T_0A_0 \gneq g -1 - \dim S$. Hence $\varphi$ is quasi-finite
dominant morphism which shows the claim above.
%For any point $x\in X_{\textnormal{reg}}$, we have $$T_xX_{\textnormal{reg}}\cong \C^{g-d}\subset T_xA\cong H^0(A, \Omega_A^1)^{\vee}\cong \C^g.$$
%Hence we have the following diagram 
%$$\xymatrix{
%\mathbb{P}T^*_{X_{\textnormal{reg}}}A \ar[d]^{\pi} \ar@{^{(}->}[r]^-i
%&X_{\textnormal{reg}}\times \mathbb{P}H^0(A, \Omega_A^1)^{\vee}\ar[dl] \ar@{->>}[r]^-p&\mathbb{P}H^0(A, \Omega_A^1)^{\vee} \\
%X_{\textnormal{reg}}
%}.$$
%We then denote $S$ be the image of $\mathbb{P}T^*_{X_{\textnormal{reg}}}A$ in $\mathbb{P}H^0(A, \Omega_A^1)^{\vee}$ through the map $p\circ i$ in the above diagram. Notice that it suffices to show $S$ is dense in $\mathbb{P}H^0(A, \Omega_A^1)^{\vee}$ if $X$ is not fibred by tori and $\dim X>0$.  
%
%Noticed that $S$ is irreducible, since $X$ is irreducible. By contradiction we assume $S$ is not dense in $\mathbb{P}H^0(A, \Omega_A^1)^{\vee}$. Denote $m:=\dim S$. Claim that $\dim S=m>0$. In fact, if $m=0$, then there is a nontrivial holomorphic 1-form $\eta$ corresponding to $s\in S$ such that the restriction $\eta|_X=0$. Also, notice that since $\dim S=0,$ $\dim X=g-1$. Also, since $X$ is not fibred by tori, $X$ generates the whole abelian variety $A$. Then this implies $\eta=0$, which is a contradiction. 
%
%Then for a general point $s\in S$, $$\dim (p\circ i)^{-1}(s)=g-m-1>0,$$ hence $$\dim \pi((p\circ i)^{-1}(s))=g-m-1>0.$$ We denote $Z_s:= \pi((p\circ i)^{-1}(s))\subset X_{\textnormal{reg}}$. For each $Z_s$, we consider the nontrivial subabelian variety $A_s:=\langle Z_s \rangle$ generated by $Z_s$.  Notice first $A_s$ is a proper subabelian variety, because for general $x\in Z_s$, and the line $L_s\subset \mathbb{P}H^0(A, \Omega_A^1)^{\vee}$ corresponding to $s$, we have $$T_x(Z_s)\subset T_xX_{\textnormal{reg}}\subset L_s^{\perp}.$$
%Since $A$ only contains at most countably many subabelian varieties and $S$ is irreducible, we have for general $s\in S$, $A_s$ are isomorphic to each other.  We denote this subabelian variety to be $A_0$ with a chosen origin $e$. Notice first that $T_e(A_0)$ is perpendicular to all $L_s$, since it is true for general $s$. Also, notice that since $X$ is not fibred by tori, $Z_s$ is a proper subvariety of the translated tori $A_0+x$ for general $s$ and any $x\in Z_s$ (Notice that $A_0+x$ does not depend on the choice of $x\in Z_s$). Thus $\dim A_0>g-m-1$, i.e., $\dim T_eA_0\geq g-m$. However, $\dim \bigcup_{s\in S}L_s=m+1$ ($\dim S=m$). So $T_e(A_0)$ cannot perpendicular to all $L_s$ for $s\in S$. This proves $S$ is dense in $\mathbb{P}H^0(A, \Omega_A^1)^{\vee}$ and hence the lemma.

\end{proof}









\section{Stratification of morphisms after Migliorini and Shende}

For a morphism $f: X\to A$ as in Theorem \ref{main1},  we consider the following diagram 
%$$\xymatrix{
%T^*X 
%& X\times_Y T^*Y \ar[l]_-{df} \ar[r]^-{\tilde{f}} &T^*Y
%},$$
\begin{center}
\begin{tikzcd}
	X\times f^*H^0(A, \Omega_A^1) \ar[r, "df"] \ar[d, "\tilde{f}"] & T^*X\\
	A\times H^0(A, \Omega_A^1)\simeq T^*A\dar["\pr_2"]\\
	H^0(A, \Omega_A^1)
\end{tikzcd}
\end{center}
 where $T^*X$ and $T^*A$ are the holomorphic cotangent bundles, 
$df$ is the usual differential. Then note
that $pr_2\tilde{f}(df^{-1}(0_X))$ is precisely the 
set of 1-forms of the form $f^*\omega$ for $\omega\in H^0(A, \Omega_A^1)$ such that $f^*\omega$ admits zeros on $X$,
i.e.\
\[V(f) = pr_2(f_{\dagger}(0_X))\]
where following \emph{loc.\ cit.} we write $f_{\dagger} = f\times \id)\circ df^{-1}$ and $0_X = T_X^*X$ is the zero section
of the cotangent bundle. 

We are now ready to state Migliorini and Shende's
result \cite{MiSh} in the form that will be useful in the proof of our Theorem \ref{main1} and Theorem \ref{thm:smoothness}.

\begin{definition}[Migliorini and Shende]\label{def:higherdiscriminants}
Let $f: X\to Y$ be a proper morphism between smooth algebraic  varieties $X$ and $Y$. The higher discriminants of $f $ are defined to be
$$\Delta^i(f):=\{ y\in Y\ |\ \textnormal{no}\ (i-1)\textnormal{-dimensional subspace of}\  T_yY \ \textnormal{is transversal to} \ f \},$$ for each nonnegative integer $i$.
\end{definition}

\begin{remark}
(1) In the above definition an $i$-dimensional subspace $W$ of $T_yY$ is transversal to $f$ means $$df_x(T_xX)+W=T_yY,$$ for any closed point $x\in f^{-1}(y)$. 

(2) By definition, $\Delta^1(f)$ is the usual discriminant, i.e., the locus in $Y$ such that $f$ is not smooth. Also by \cite[Proposition 10.6]{Har77}, we have the filtration  $$Y=\Delta^0(f)\supset \Delta^1(f)\supset\Delta^2(f)\supset\Delta^3(f)\supset\ldots.$$

(3) $\Delta^i(f)$ are closed subvarieties of $Y$, which measure how singular $f$ can be.
\end{remark}



\begin{theorem}[Migliorini, Shende]\label{MiSh}
Let $f: X\to Y$ be a proper morphism between smooth algebraic varieties $X$ and $Y$. Then $$\tilde{f}(df^{-1}(0_X))=\bigcup_{i\geq0}\overline{T^*_{D^i(f)_{\textnormal{reg}}}Y},$$ where $0_X$ is the zero section of the cotangent bundle $T^*X$, and $\overline{T^*_{D^i(f)_{\textnormal{reg}}}Y}$ is the closure of the conormal bundle of the smooth locus $D^i(f)_{\textnormal{reg}}$ of codimension $i$ components  $D^i(f)$ of $\Delta^i(f)$ in $Y$.
\end{theorem}

Since the codimension $i$ components $D^i(f)$ of $\Delta^i(f)$ will be used for many times, we give the following definition.

\begin{definition}
Let $f: X\to Y$ be a proper morphism between smooth algebraic varieties $X$ and $Y$. The pure $i$-th discriminants of $f $ are defined to be
the union of codimension $i$ components of $\Delta^i(f)$, denoted by $D^i(f)$.
\end{definition}

From now on we will focus on a morphism $f: X\to A$ from smooth projective variety $X$ to abelian variety $A$. Also, we fix the following notation
$$\xymatrix{
T^*X
& X\times T_eA \ar[l]_-{df} \ar[r]^-{\tilde{f}} &T^*A\ar@{->>}[r]^-p& T^*_e A=H^0(A, \Omega_A^1)
},$$ where $T_eA$ is the tangent space of $A$ at a chosen origin $e$. Notice first $p(\tilde{f}(df^{-1}(0_X)))$ is exactly the set of holomorphic 1-forms $\omega\in H^0(A, \Omega_A^1)$ such that $f^*\omega$ has zeros on $X$.

\begin{corollary}\label{Cor:MiShCor}
Let $f: X\to A$ be a morphism from smooth projective variety $X$ to an abelian variety. Suppose there is a nontrivial holomorphic 1-form $\omega\in H^0(A, \Omega_A^1)$ such that $f^*\omega$ has zeros. Then there exists $i\geq1$ such that the pure $i$-th discriminant $D^i(f)$ is nonempty. In other words, $f$ is smooth if and only if $D^i(f)=\emptyset$ for all $i\geq 1$.
\end{corollary}

\begin{proof}
Assume that for all $i\geq 1$, $D^i(f)=\emptyset$, then $$\tilde{f}(df^{-1}(0_X))=\overline{T^*_{D^0(f)_{\textnormal{reg}}}Y}=\overline{T^*_{\Delta^0(f)_{\textnormal{reg}}}Y}=A\times \{0\}.$$ Hence $p(\tilde{f}(df^{-1}(0_X)))=\{0\}$, i.e., the only holomorphic 1-form admitting zeros is the trivial one, which is a contradiction.
\end{proof}



\section{Generalisation and proof of Theorem \ref{thm:smooth}}


\begin{proposition}
Given a morphism $f\colon X\to A$ from a smooth 
projective variety to an abelian variety $A$, there is a holomorphic 1-form $\omega\in H^0(A, \Omega_A^1)$ such that $f^*\omega$ has no zeros if and only
if for all $i\geq1$, and the pure $i$-th discriminant $D^i(f)$ of $f$

(1) $D^i(f)$ are either empty, i.e., $f$ is smooth (by Corollary \ref{Cor:MiShCor});

(2) or each irreducible component of $D^i(f)$ is fibered by tori and of positive dimension. 
\label{thm:nonvanishing}
\end{proposition}

\begin{proof} ``$\Leftarrow$'' By Theorem \ref{MiSh}, (1) implies that for every holomorphic 1-form $\omega\in H^0(A, \Omega_A^1)$, $f^*\omega$ has no zeros. By Theorem \ref{MiSh} and Proposition \ref{van-nonsimple}, (2) implies that for general holomorphic 1-form $\omega\in H^0(A, \Omega_A^1)$, $f^*\omega$ has no zeros.


``$\Rightarrow$'' 
Suppose there is $i$ and an irreducible component $D_0^i(f)$ of $D^i(f)$ such that $D_0^i(f)$ is not fibred by tori or $\dim D_0^i(f)=0$. If $\dim D^i_0(f)=0$, then there is a point $x\in X$ so that the rank of the tangent map $Tf_x$ is 0, thus every holomorphic 1-form pulled back from $A$ vanishes at $x$, which is a contradiction. If $D_0^i(f)$ is not fibred by tori and $\dim D_0^i(f)>0$, applying Proposition \ref{van-nonsimple}, we have for general holomorphic 1-form $\omega\in H^0(A, \Omega_A^1)$, $\omega|_{D_0^i(f)_{\textnormal{reg}}}$ has zeros. Hence $$p(\overline{T^*_{D_0^i(f)_{\textnormal{reg}}}Y})=H^0(A, \Omega_A^1).$$ Hence $$p(\tilde{f}(df^{-1}(0_X)))=H^0(A, \Omega_A^1),$$ i.e.,$$V(f)=f^*H^0(A, \Omega_A^1),$$ which is a contradiction.
\end{proof}

\sorry{This is a strengthening of a ``special case" of Stefan's Theorem 1.4 (2)}



\begin{proof}[Proof of Theorem \ref{thm:smooth}]
``$\Rightarrow$'' is trivial.

``$\Leftarrow$'' Assume $f$ is not smooth, then there is a holomorphic 1-form has zeros. Then there exist $i\geq 1$ such that $D^i(f)$ is nonempty by Corollary \ref{Cor:MiShCor}. Since $A$ is simple, $\omega|_{D^i(f)_{reg}}$ has zero for general holomorphic 1-forms $\omega\in H^0(A, \Omega_A^1)$ by \cite[Proposition 3.1]{HK05}, i.e.,  $p(\overline{T^*_{D^i(f)_{\textnormal{reg}}}A})=H^0(A, \Omega_A^1)$, which means every holomorphic 1-form pulled back from $A$ has zero.
\end{proof}


\begin{remark}
(1) {\color{red}TBA If the albanese variety of $X$ is simple, then Theorem A implies Kotschick's conj.........}

(2) {\color{red} TBA conterexample $E_1\times E_2\times E_3$ and blowup translated $E_1$ and $E_3$............}
\end{remark}





\section{Proof of Theorem {\ref{main}}: Linearity of holomorphic 1-forms with zeros} 
For any subvariety $X$ of an abelian variety $A$, we consider the following diagram 
$$\xymatrix{
T^*_{X_{\textnormal{reg}}}A\ar@{->>}[r]^-p& T^*_e A=H^0(A, \Omega_A^1)
},$$ where $p$ is the projection given by moving the cotangent vectors to $T^*_eA$ via group action. Notice that $p(T^*_{X_{\textnormal{reg}}}A)$ is exactly the set of holomorphic 1-forms in $H^0(A, \Omega_A^1)$ whose restriction on $X_{\textnormal{reg}}$ admitting zeros. Then we have the following corollary of Proposition \ref{van-nonsimple}.

\begin{corollary}\label{Main-coro}
Let $i: X\to A$ be a irreducible subvariety of an abelian variety $A$. Then $\overline{p(T^*_{X_{\textnormal{reg}}}A)}$ is linear. 
\end{corollary}


\begin{proof}
By Poincar\'e complete reducibility theorem, after passing to a \'etale covering $\tau:A'\to A$ we have a Cartesian diagram 
$$\xymatrix{
X'\ar[r]\ar@{^{(}->}[d]^-{i'}& X\ar@{^{(}->}[d]^-{i}\\
A'\ar[r]& A},$$ and we may assume $A'\cong B\times C$ with $B$ and $C$ being abelian varieties, $X'\cong Y\times C$ with $Y\subset B$ being a subvariety which is not fibred by tori in B. Then we have $$T^*_{X'_{\textnormal{reg}}}A'\cong T^*_{Y_{\textnormal{reg}}}B\times C.$$ As the above, we denote $p'$ be the natural projection $$\xymatrix{
T^*_{X'_{\textnormal{reg}}}A'\ar@{->>}[r]^-{p'}& T^*_e A'=H^0(A', \Omega_A'^1)
}.$$  Then by Proposition \ref{van-nonsimple}, we have $\overline{p'(T^*_{X'_{\textnormal{reg}}}A')}=H^0(B, \Omega_B^1)$, which is linear. Hence $\overline{p(T^*_{X_{\textnormal{reg}}}A)}$ is linear, since $X'\to X$ is \'etale.
\end{proof}

Next we will use Corollary \ref{Main-coro} and Theorem \ref{MiSh} to prove our first main result Theorem \ref{main1}.
\begin{corollary}\label{ECNT}
For $X$ being a smooth projective variety $X$ such that the topological Euler characteristic class $\chi(X)\not=0$, $V(X)$ is a linear subvariety.
\end{corollary}

\begin{proof}[Proof of Theorem \ref{main1}]
%For the morphism $f: X\to A$, we consider the following diagram 
%$$\xymatrix{
%T^*X
%& X\times T_eA \ar[l]_-{df} \ar[r]^-{\tilde{f}} &T^*A\ar@{->>}[r]^-p& T^*_e A=H^0(A, \Omega_A^1)
%},$$ where $T_eA$ is the tangent space of $A$ at a chosen origin $e$. Notice first $p(\tilde{f}(df^{-1}(0_X)))$ is exactly the set of holomorphic 1-forms $\omega\in H^0(A, \Omega_A^1)$ such that $f^*\omega$ has zeros on $X$.  
By Theorem \ref{MiSh}, we have $$\tilde{f}(df^{-1}(0_X))=\bigcup_{i\geq0}\overline{T^*_{D^i(f)_{\textnormal{reg}}}Y},$$ where $\overline{T^*_{D^i(f)_{\textnormal{reg}}}Y}$ is the closure of the conormal bundle of the smooth locus $D^i(f)_{\textnormal{reg}}$ of pure $i$-th discriminant $D^i(f)$. By Corollary \ref{Main-coro}, we have $p(\overline{T^*_{D^i(f)_{\textnormal{reg}}}Y)}=\overline{p(T^*_{D^i(f)_{\textnormal{reg}}}Y)}$ is linear. Hence $$p(\tilde{f}(df^{-1}(0_X)))=\bigcup_{i\geq0}p(\overline{T^*_{D^i(f)_{\textnormal{reg}}}Y})$$ is linear. Also, by the proof of Corollary \ref{Main-coro}, it is clear that each irreducible component of $V(f)$ are $\Q$-sub Hodge structures associated to subtori which are generated by $D^i(f)$.
\end{proof}




{\color{red} Add two corollaries, the above main theorem implies the main theorems of [Papa Schnell], [Hacon Kovacs]}





%\section{Holomorphic Tischler's theorem}


%\begin{lemma}\label{Lem:inclusion-fiber-by-tori}
%Let $A$ be any abelian variety. Let $Y_1\times B_1$ and $B_2$ be two subvarieties of $A$, where $Y_1$ is not fibred by tori, $B_2$ is a simple abelian variety and $B_1$ is an abelian variety. Suppose $B_2\subset Y_1\times B_1$. Then $B_2$ is a simple factor of $B_1$ upto isogeny.
%\end{lemma}

%\begin{proof}
%It suffices to show that the natural map $p: B_2\to Y_1\times B_1\to Y_1$ maps $B_2$ to a point. Assume not, then we have a positive dimensional abelian variety $C:=p(B_2)$ contained in $Y_1$. Then we consider the inclusion $$C\subset Y_1\subset A.$$ Without losing of generality we can assume that $C$ contains a chosen origin $0$ by translating $C\subset Y_1$ using group action if necessary. Then we want to find contradiction from  $$0\in C\subset Y_1\subset A,$$ where $Y_1$ is not fibred by tori.

%TBA
%\end{proof}

%With Lemma \ref{Lem:inclusion-fiber-by-tori} and the above theorem we prove, then we have the following strong result.

%\begin{theorem}
%Let $X$ be any smooth complex projective variety. Then $X$ admits a nowhere vanishing holomorphic 1-form $\omega$ if and only if $X$ admits a smooth morphism to positive dimensional abelian variety $A$
%\end{theorem}

%\begin{proof}
%``$\Leftarrow$'' is trivial.

%``$\Rightarrow$'' Consider the albanese map $a: X\to A_X$ of $X$. By assumption we have a holomorphic 1-form $\omega\in H^0(A_X, \Omega_{A_X}^1)$ such that $a^*\omega$ is nowhere vanishing. By Corollary \ref{Cor:MiShCor}, we may assume that not all $D^i(f)$ are empty for $i\geq 1$. %After passing to \'etale covering $\tau: A\to A_X$, we have the following  Cartesian diagram 
%$$\xymatrix{
%X'\ar[r]\ar[d]^-{f}& X\ar[d]^-{a}\\
%A\ar[r]^{\tau}& A_X},$$ $A'=A_1\times\ldots A_m$ being product of simple abelian varieties $A_i$, and a holomorphic 1-form $\omega'\in H^0(A, \Omega_{A}^1)$ such that $f^*\omega'$ is nowhere vanishing.
%Then by Theorem \ref{thm:nonvanishing}, we get all the nonempty pure $i$-th discriminants $D^i(a)$ are fibred by tori and $\dim D^i(a)>0$. Noticed also, by ({\color{red} Hartshorne generic smooth}), we claim$$D^i(a)\supset D^j(a),$$ if $j>i$ and $D^i$ and $D^j$ are nonempty pure $i$-th discriminants in $\{D^k(a)\}_{k=1}^{g}$, where $g=\dim A$. {\color{blue}  I Need to think about this, which seems not OK! } Assume the highest nontrivial discriminant is $D^m(a)$, which is fibred by tori, then we can take simple abelian subvariety$A_0$ of $A_X$ so that $A_0$ is a factor of the torus part of  $\Delta^m(a)$. By Lemma \ref{Lem:inclusion-fiber-by-tori}, $A_0$ is a factor of all the discriminants. Notice that there is a \'etale covering $\tau: A_X\to A_0\times B$ with $B$ another abelian variety. Then from the proof of Corollary \ref{Main-coro}, we have all the nontrivial holomorphic 1-forms in $(\tau\circ a)^*H^0(A_0, \Omega_{A_0}^1)$ has no zeros on $X$. But since $A_0$ is simple, we have $\tau\circ a: X\to A_0$ is smooth by Theorem \ref{thm:smooth}.   
%\end{proof}

%{\color{red}(This theorem covers theorem A, remember to replace this as Theorem A)}



\section{Linearity of holomorphic 1-forms with codimension one zeros}

In this section, we consider (logarithmic) holomorphic 1-forms with codimension one zeros. We will prove that $V^1(X)$ is linear and give a more finer analysis on $V^1(X)$. 

\subsection{Projective case}

%We give some preliminaries, which is used in studying (logarithmic) holomorphic 1-forms with codimension one zeros, especially the linearity and finer structure of $V^1(X)$. 

First we recall the definition of cohomology jump loci. Let $X$ be a connected finite CW-complex with $\pi_{1}(X)=G$. Then we have the Betti moduli of rank one local system $\textnormal{M}_B(X):= \Hom(G,\C^{\ast})$ is a commutative affine algebraic group. Each character $\rho \in \textnormal{M}_B(X)$ defines a rank one local system on $X$, denoted by $L_{\rho}$. The tangent space $T_1\textnormal{M}_B(X)$ of $\textnormal{M}_B(X)$ at trivial local system 1 is canonically isomorphic to $H^1(X, \C)$.
The cohomology jump loci of $X$ are defined as follows:
$$\mathcal{S}^i(X)=\lbrace \rho\in \textnormal{M}_B(X) \mid  H^{i}(X, L_{\rho})\neq 0 \rbrace,$$ 
which by the structure theorem are finite union of torsion translated subtori of $\textnormal{M}_B(X)$.

To study $V^1(X)$ we introduce a homotopy invariant of $X$, denoted by $T^1(X)${\color{red} (The name TBA, translated tangent cone?)}, which is contained in $H^1(X, \C)$. The following definition of $T^1(X)$ is based on Arapura's work. Roughly speaking, Arapura \cite{Ara97} showed that every positive dimension component of $\mathcal{S}^1(X)$ can be induced by a so called strict orbifold map. A morphism $f:X\to C$ from $X$ to a smooth projective curve $C$ is called a  {\it strict orbifold map} if $f $ is surjective, has connected fibers and one of the following condition holds:
\begin{itemize}
\item $g(C)\geq 2$
\item $g(C)=1$ and $f$ has at least one multiple fiber.
\end{itemize}
A strict orbifold map always induces an injective map: $f^*: H^1(C, \C) \to H^1(X,\C)$. In fact, there are only at most finitely many equivalent strict orbifold maps. Define $$T^1(X):= \bigcup_f \im f^*,$$
where the union runs over all possible strict orbifold maps for $X$. By another equivalent definition of Budur-Wang-Yoon \cite{BWY16} , $T^1(X)$ is a linear subvariety, which is the union of torsion translation of affine tangent space of each component of degree 1 cohomology jump loci $\mathcal{S}^1(X)$. We denote the holomorphic part of the tangent cone $T^1(X)$ to be $T^1_h(X)$, i.e., $T_h^1(X):=T^1(X)\cap H^0(X, \Omega_X^1)$, which is a linear subvariety.

We will see that except for $T_h^1(X)$, another part of $V^1(X)$ is coming from negative divisors.
\begin{definition}
Let $X$ be a smooth projective variety of dimension $n$, with a fixed very ample line bundle $H$ and a prime divisor $E$ on $X$. We say that $E$ is $H$-negative if $E^2\cdot H^{n-2}<0$, where $$E^2\cdot H^{n-2}=\int_X c_1^2(E)\wedge c_1(H)^{n-2}.$$ Similarly we can define $H$-trivial and $H$-positive divisors corresponding to the above integration is zero and positive, respectively. We say $E$ a negative (trivial or positive respectively) if it is $H$-negative ($H$-trivial or $H$-positive respectively) for all ample divisor $H$.
\end{definition}  
With the above definition, we define $$V_{H\textnormal{-neg}}(X):=\{\omega\in H^0(X, \Omega_X^1)\ |\ \omega(p)=0\  \textnormal{for any point}\ p\in E, \ \textnormal{with $H$-negative divisor}\  E\}$$  

\begin{lemma}\label{lem:welldef}
Let $E$ be a integral divisor in $X$ with $\dim X=n$. Suppose there exists a holomorphic 1-form $\omega$ such that $\omega(p)=0$ for each $p\in E$. Then the sign of the intersection number $E^2\cdot H^{n-2}$does not depend on the choice of ample divisor $H$.
\end{lemma}

\begin{proof}
By Theorem \cite[Theorem 2]{Sp88}, $E^2\cdot H^{n-2}\leq 0$ for any ample divisor $H$ and when $E^2\cdot H^{n-2}=0$, $E$ is set theoretically contained in a fibre of a strict orbifold map $f: X\to C$ to a smooth projective curve $C$.  Claim that $E$ is the only component of the fiber containing $E$ if $E^2\cdot H^{n-2}=0$ for some ample divisor $H$. In fact, assume there is an effective divisor $E':=f^{-1}(f(E))\backslash E$ such that $aE+bE'$ is linearly equivalent to $F$ with $F$ a general fiber of $f$ and $a$, $b$ are positive integers. Since $f$ has connected fibres, $E\cdot E'\not=0$.  First notice that $(aE+bE')\cdot E'\cdot H^{n-2}=0$. Also, $(aE+bE')^2\cdot H^{n-2}=0$. Hence we get $E^2\cdot H^{n-2}<0$, which is a contradiction. Since set theoretically $E$ is the whole fiber of a morphism $f: X\to C$, $E^2\cdot H^{n-2}=0$ for all ample divisor $H$. 
\end{proof}


With the Lemma \ref{lem:welldef}, we have the following well defined notation$$V_{\textnormal{neg}}(X):=V_{H\textnormal{-neg}}(X)\subset H^0(X, \Omega_X^1),$$ where $H$ is any ample divisor of $X$. With the above notations, we have the following theorem which is based on Spurr \cite[Theorem 2]{Sp88}.

\begin{theorem}\label{Thm:Proj-codim1}
 Let $X$ be a complex smooth projective variety, with the above notations, we have that 
$$V^1(X)= T_h^1(X)\cup V_{\textnormal{neg}}(X).
$$
Every irreducible component of $V^1(X)$ is a linear complex subvector space of $H^0(X, \Omega_X^1)$, i.e., $V^1(X)$ is a linear subvariety. %Moreover, $V_{\textnormal{neg}}(X)$ is a union of  one dimensional complex vector spaces of $H^0(X, \Omega_X^1)$.
\end{theorem}

\begin{remark} (1) The Theorem \ref{Thm:Proj-codim1} complements the result of Green-Lazarsfeld \cite{GL87}: $T_h^1(X) \subset V^1(X)$. In general one should not expect $T_h^1(X) = V^1(X)$. Let $X$ be a complex abelian surface and $Y$ be the blowup of $X$ along a point. Then $T_h^1(X)=T_h^1(Y)$, but  $V^1(X)\subsetneq V^1(Y)$.

(2) In dimension 2, \cite[Theorem 2]{Sp88} also holds for compact K\"ahler surface and even any compact complex surface. For the compact complex surface $X$, it is not clear if $V^1(X)$ has finitely many components, since it is not algebraic in general.

(3) The two parts $T_h^1(X)$ and $V_{\textnormal{neg}}(X)$ may have overlap. For example if $f: S\to C$ is a morphism from a smooth complex projective surface $S$ to a smooth projective curve $C$ with genus $g(C)\geq2$. Take a holomorphic 1-form $\omega\in H^0(C, \Omega_C^1)$ which has a zero $p\in C$. Pick any point $s\in S$ over $p$ and blow up $S$ along $s$ with $(-1)$ curve $E$. Then consider the natural morphism $f': S'\to C$, then $f^*\omega(E)=0$ and hence $f^*\omega\in T_h^1(X)\cap V_{\textnormal{neg}}(X)$.
\end{remark}

\begin{lemma} \label{countable} Let $X$ be a $n$-dimensional smooth complex projective variety with very ample divisor $H$. Then there are at most countablely many $H$-negative divisors in $X$.
\end{lemma}

\begin{proof}
Let $E$ be any $H$-negative divisor. After fixing $n-2$ general hyperplanes $H_1, \ldots, H_{n-2}$ in the linear system $|H|$, we have over the complete intersection surface $S:=H_1\cap H_2\cap\ldots\cap H_{n-2}$, $E\cap S$ is a negative curve in $S$, which has no infinitesimal deformation, i.e., the $H^0(E\cap S, N_{E\cap S/S})=0$, where $N_{E\cap S/S}$ is the normal bundle of $E\cap S$ in $S$. Then they are isolated points in the Hilbert scheme $\textnormal{Hilb}_S^{P(m)}$ with some Hilbert polynomial{\color{red}(Hartshorne deformation theory reference)}. Note also that $\textnormal{Hilb}_X^{P(m)}$ is of finite type and $P(m)$ are polynomials with $\Q$ coefficients. Hence there are at most countably many negative curves on $S$ with above properties. Hence there are at most countably many $H$-negative divisors.
\end{proof}

\begin{proof}[Proof  of theorem \ref{Thm:Proj-codim1}]
{\color{red}(Remember to discuss the case $\dim X=1$ case, after merging.)}With the notation in theorem \ref{Thm:Proj-codim1},  for any holomorphic 1-form $\omega\in V^1(X)$, there is a integral divisor $D\subset X$ such that $\omega(D)=0$. Then by \cite[theorem 2]{Sp88}, we have either $D$ is $H$-negative or $H$-trivial for any chosen ample divisor $H$. If $D$ is $H$-negative for any ample divisor $H$ then $\omega\in V_{\textnormal{neg}}$. Still by \cite[theorem 2]{Sp88}, If $D$ is $H$-trivial for some ample divisor $H$, then $D$ is contained in a fiber of a morphism $f: X\to C$ with $C$ a smooth projective curve of positive genus and $f$ admitting connected fibers, and $\omega=f^*\eta$ for $\eta\in H^0(C, \Omega_C^1)$. Claim that $D$ is the whole fiber. In fact, if we denote $F:=f^{-1}(f(D))$ and assume by contradiction that $F=D\cup D'$ with $D'\not=\emptyset$. Then the intersection number $D'\cdot D\cdot H^{n-2}>0$. Also, note that $F\cdot D\cdot H^{n-2}=0$, thus $D^2\cdot H^{n-2}<0$, which is a contradiction. Since $D$ is a zero set of a form $\omega$ pullback from $C$ and $D$ is the whole fiber, thus (1) $D$ is multiple and genus $g(C)=1$ or (2) $g(C)>1$ and $\eta(f(D))=0$. Hence $f$ is a strict orbifold fibration. Then $\omega\in T_h^1(X)$. Notice that $T_h^1(X)\subset V^1(X)$ by \cite{GL87}. Hence $$V^1(X)= T_h^1(X)\cup V_{\textnormal{neg}}(X).
$$
By lemma \ref{countable}, $V_{\textnormal{neg}}$ is a union of at most countably many linear subspaces in $H^0(X, \Omega_X^1)$ of the following type $$V_E(X):=\{\omega\in H^0(X, \Omega_X^1)\ |\ \omega(p)=0\  \textnormal{for any point}\ p\in E\},$$ where $E$ is a negative divisor. Since $V^1(X)$ is an algebraic set and $T_h^1(X)$ is a linear subvariety, $V^1(X)$ is a linear subvariety.
 \end{proof} 
 
 In Theorem \ref{Thm:Proj-codim1}, we can write holomorphic 1-forms with codimension one zeros s union of two parts: The 1-forms in the {\color{red} translated tangent cone?} and the one vanishes along a negative divisor.  Another way to understand  $V^1(X)$ is one can divide $V^1(X)$ into set of resonant 1-forms $$V^1_r(X):=V^1(X)\cap R_h(X),$$ and set of nonresonant 1-forms with codimension one zeros, denoted to be $V^1_{nr}(X)$, which is locally closed. Notice that $V_r^1(X)$ is a linear subvariety, since $V^1(X)$ is linear by Theorem \ref{Thm:Proj-codim1}  and $R_h(X)$ is linear by Theorem \ref{thm: resonant}. For holomorphic nonresonant 1-forms,  we have the following proposition.
 \begin{proposition}
Let $X$ be a smooth complex projective variety of dimension $n$. There are only finitely many integral divisors $D$ on $X$, such that there is a holomorphic nonresonant 1-form $\omega\in H^0(X, \Omega_X^1)$ with $\omega(D)=0$.
 \end{proposition}
 
 \begin{proof}
For any holomorphic nonresonant 1-form $\omega$ such that the zero set $Z(\omega)$ contains a integral divisor $D\subset X$, by Theorem \ref{thm:stefan} (1), $H^{n-1}(D, {\omega_X}|_D)=0$, where $\omega_X$ is the canonical line bundle of $X$. Hence $H^0(D, N_{D/X})=0$ by Serre duality. Then by the same Hilbert scheme argument as that is the proof of   Lemma \ref{countable}, we have there are at most countably many integral divisors that are contained in zero locus of some holomorphic nonresonant 1-forms.  Notice also since $V^1(X)$ is algebraic and $V^1_{nr}(X)=V^1(X)\backslash V_r^1(X)$ is open in $V^1(X)$, $\overline{V_{nr}^1(X)}$ has finitely many irreducible components. Since $$\overline{V_{nr}^1(X)}=\bigcup_{D}V_D(X),$$ where the union runs over all integral divisors $D$ contained in zero loci of holomorphic nonresonant 1-forms. Hence the proposition holds.
 \end{proof}
 
 \begin{remark}
By the H.-Y. Lin and Schreieder \cite[appendix]{SS19}, the zero set of any universal nonresonant 1-form is of codimension at least two. 
 \end{remark}

 To end this subsection, we consider nonresonant 1-forms on surfaces, which is for its own interest. Let $S$ be smooth complex surface, one can bound genus of curves along which a nonresonant 1-form may vanish.
 
 \begin{proposition}
 Let $S$ be smooth complex projective surface and $C$ be a curve on $S$. Suppose there is a nonresonant holomorphic 1-form $\omega\in H^0(S, \Omega_S^1)$ such that $\omega(C)=0$ Then $C$ is a rational curve or an elliptic curve.
 \end{proposition}
 
 
 \begin{proof}
 Since $C\subset Z(\omega)$, we have $H^1(C, {\omega_S}|_C)=0$ by Theorem \ref{thm:stefan} (1). Consider the normalization $\eta: \widetilde{C}\to C$ and the exact sequence $$0\to \mathcal{O}_C\to \eta_*\mathcal{O}_{\widetilde{C}}\to \delta\to 0, $$ where $\delta$ is the skyscraper sheaf defined as the coker. Then we have the short exact sequence $$0\to {\omega_S}|_C\to \eta_*{{\omega_X}|_{\widetilde{C}}}\to \delta\to 0.$$ Then we get $$\dim H^0(\widetilde{C}, {\omega_X}|_{\widetilde{C}})\leq \dim H^0(\delta);   H^1(C, {\omega_S}|_C)=H^1(\widetilde{C}, {\omega_X}|_{\widetilde{C}})=0.$$ By Riemann-Roch, $$\deg {\omega_X}|_{\widetilde{C}}+1-g(\widetilde{C})\leq \dim H^0(\delta).$$ Notice also, $$p_a(C)=g(\widetilde{C})+\dim H^0(\delta), $$ and by genus formula $$\deg {\omega_X}|_{\widetilde{C}}+C^2=2p_a(C)-2.$$ Then by \cite[Theorem 1]{Sp88}, $C^2\leq 0$. Hence $p_a(C)\leq1$.
 \end{proof}
 

 \subsection{Quasi-projective case}
 

Let $U$ be a smooth complex quasi-projective variety. Let $X$ be a good compactification of $U$, i.e., a smooth compactification of $U$ with boundary $D:=X-U$ a simple normal crossing divisor. Note that the space of logarithmic 1-forms $H^0(X, \Omega_X^1(\log D))$ does not depend on the choice of the good compactification, so we may denote it by $W(U)$. We write $H^0(X, \Omega_X^1(\log D))$ when we want to emphasize the boundary divisor. Similar to projective case,  one can define $$V^i(X,D):=\{ \omega\in H^0(X, \Omega_X^1(\log D)) \mid \codim_X Z(\omega) \leq i \}.$$
where $Z(\omega)$ is the zero locus of $\omega$. Again by Chevalley's upper-semicontinuity theorem, $V^i(X, D)$ are all algebraic sets.

\begin{remark} For a smooth quasi-projective variety $U$, $V^i(X,D)$ clearly depends on the good compactification $(X,D)$. For example, let $X$ be a smooth projective variety admitting a holomorphic 1-form $\omega\in H^0(X, \Omega_X^1)$ with isolated zero set. Let $D\subset X$ be a divisor containing one point $p \in Z(\omega)$, and $Y$ be the blowup of $X$ along $p$ with exceptional divisor $E$. Then $V^1(X, D)\subsetneq V^1(Y, D\cup E)$. To get an invariant of $U$, we define
$$V^i(U)= \bigcap_{(X,D)} V^i(X,D) ,$$
where the intersection runs over all possible good compactification $(X,D)$ of $U$. Clearly, $V^i(U) $ are closed algebraic varieties of $W(U)$.
\end{remark} 

For a good compactfication $(X,D)$ of $U$ where $D=\cup_{j=1}^r D_j$. Set $$V_{\textnormal{bound}}(X, D):= \{\omega\in H^0(X, \Omega_X^1(\log D)) \mid D_j \subset Z(\omega)\  \text{ for some }\  j \}.$$ Similar to projective case, we denote for a subvariety $E$, $$V_E(X, D):=\{\omega\in H^0(X, \Omega_X^1(\log D)) \mid  E \subset Z(\omega) \}$$ and 
 $$V_{\textnormal{neg}}(X, D):= \bigcup_E V_E(X, D),$$ where the union runs over all the negative divisor $E$ in $X$ such that $E$ is not contained in $D$. 
 
Define $$T_h^1(X, D):= \bigcup_f f^*H^0(C, \Omega_C^1(\log B)),$$
where the union runs over all possible surjective morphism $f: X-D\to C$ to a smooth quasi-projective curve $C=\bar{C}-B$ ($B$ can be empty), such that $f$ has  connected fibers, and one of the following condition holds when $C$ is projective:
\begin{itemize}
\item $g(C)\geq 2$
\item $g(C)=1$ and $f$ has at least one multiple fiber.
\end{itemize} 
{\color{red} (Check the correctness on poles and zeros for $g(C)=0,1$)} 
 
\begin{theorem} \label{thm:codim1quasiprojective} Let $(X, D)$ be a pair consists of an $n$-dimensional smooth complex projective variety $X$ and a simple normal crossing divisor $D$ with irreducible components $\{D_j\}_{j=1}^r$. Then 
$$
V^1(X,D)= T^1_h(X, D) \cup V_{\textnormal{neg}}(X, D) \cup V_{\textnormal{bound}}(X, D),
$$
and every irreducible component of $V^1(X,D)$ is a linear subvector space of $H^0(X, \Omega_X^1(\log D))$. 
\end{theorem}

In order to show the above theorem, we first generalize Spurr \cite[Theorem 2]{Sp88} and ideas of the proof to quasi-projective varieties. 

\begin{proposition} \label{Prop:Spurr-no-intersection}
Let $(X, D)$ be a pair with $X$ a smooth complex projective variety and $D$ a simple normal crossing divisor of $X$. Let $H$ be an ample divisor on $X$. Suppose $(X, D)$ carries a nontrivial logarithmic 1-form $\omega\in H^0(X, \Omega_X^1(\log D))$  which restricts to zero on an integral divisor $E$ with $E^2\cdot H^{n-2}\geq0,$ and $E\cap D=\emptyset,$ then there is a surjective morphism $f: X-D\to C$ to a smooth quasi-projective curve $C=\bar{C}-B$ ($B$ can be empty) with 

(1)  $\omega=f^*\eta$ for some $\eta\in H^0(C, \Omega_C^1(\log B))$.

(2) $f$ has connected fibers.

(3) $E$ is contained in the fiber of $f$ and $E^2\cdot H^{n-2}=0$.
\end{proposition}

\begin{proof}
Firstly, we prove the theorem in the case $\dim X=2$. We may assume that $\omega$ is not everywhere holomorphic, otherwise we are done by \cite[Theorem 1]{Sp88}.

Denote $U=X-D$. Let $\phi: N\to E$ be the normalization map and $\varphi: N\to U$ be the natural map ($E\cap D=\emptyset$). After choosing base points $a\in N$ and $\varphi(a)\in U$, we have the following diagram 
$$
\xymatrix{
 N\ar[r]^{\varphi}\ar[d]^{\alpha_N}& U \ar[d]^{\alpha_U} \\
  A_N\ar[r]^{\psi} & A_U,}
$$ where $\alpha_N$ and $\alpha_U$ are albanese maps for the chosen base points $a$ and $\varphi(a)$, and $\psi$ is induced by universal property of albanese map of $N$. Following the construction of $A_U$, we pick a basis $\{\theta_1,\ldots\theta_q\}$ for $H^0(X, \Omega_X^1)$ and $\{\omega_1, \ldots, \omega_r\}\in H^0(X, \Omega_X^1(\log D))$ such that $\{\theta_1, \ldots, \theta_q, \omega_1, \ldots, \omega_r\}$ is a basis of $H^0(X, \Omega_X^1(\log D))$ and $\omega_1=\omega$. Also, we pick basis $\{\gamma_1, \ldots, \gamma_{2q}\}$ for $H_1(X, \mathbb{Z})$ and a basis $\{\delta_1, \ldots, \delta_r\}$ for $\ker\{ H_1(U, \mathbb{Z})\to H_1(X, \mathbb{Z})\}$. Then we have periods as a semi-lattice for $A_U$ $$\Lambda=\sum_{i=1}^{2q}\mathbb{Z}(\int_{\gamma_i}\theta_1, \ldots, \int_{\gamma_i}\omega_r)+\sum_{i=1}^r\mathbb{Z}(\int_{\delta_i}\theta_1, \ldots, \int_{\delta_i}\omega_r).$$ The the semi-albanese map $\alpha_U$ is given by $$\alpha_U(x)=[\sum_{i=1}^q(\int_{\varphi(a)}^x\theta_i)\theta^*_i+\sum_{i=1}^r(\int_{\varphi(a)}^x\omega_i)\omega_i^*]\slash\Lambda,$$ where $\theta_i^*$ and $\omega_i^*$ are the dual bases in $H^0(X, \Omega_X^1(\log D))^{\vee}$.  Now we consider the transpose of the pullback map $$\varphi^{\vee t}: H^0(N, \Omega_N^1)^{\vee}\to H^0(X, \Omega_X^1(\log D))^{\vee},$$ which induces the morphism  $\psi$. Since $\omega|_{E}=\omega_1|_{E}=0$, $\varphi^{\vee}(\omega_1)=0$. Then we get $$\varphi^{\vee t}(H^0(N, \Omega_N^1))\subset \{z_1=0\},$$ where $z_1$ is the coefficient coordinate of $\omega_1^*$. Thus we get a proper subtorus $T_0:=\psi(A_N)$ which is contained in $\{z_1=0\}/\Lambda$.  Defining $T:=A_U/T_0$, we get morphism $\beta: U\to T$.  Since we can pick a point $x\not\in E$ such that $\int_{\varphi(a)}^x\omega_1\not=0$, hence $\beta(U)$ is not constant. Also, $\alpha_U(E)=T_0$, hence $E$ is contracted by the morphism $\beta$.

Claim that $\dim\beta(U)=1$. Otherwise, we get $\beta: U\to \beta(U)$ be a generically finite morphism. Projectivize $\beta(U)$, we get a projective variety $\overline{\beta(U)}$ and rational map $U\dasharrow \overline{\beta(U)}$. Resolving the indeterminant locus, we may get a generically finite morphism $\overline{\beta}:\overline{U}\to\overline{\beta(U)}$ with $\overline{U}$ smooth and projective. %{\color{blue} and $\overline{U}-U$ a simple normal crossing divisor}. 
Note that resolving the indeterminant locus does not affect $E$, since $E\cap D=\emptyset$. Hence $E^2<0$ in $\overline{U}$ (See e.g., \cite[Theorem 10.1]{KK}). Note that $\overline{U}$ does not need to be $X$. However, $E^2$ being negative only depends on the normal bundle of $E$ in $U$. However, this contradicts the assumption $E^2\geq 0$. 

Taking the Stein factorization, we get the following commutative diagram:
$$\xymatrix{
\overline{U} \ar[rd] \ar[r]^f & \overline{ C} \ar[d]  \\
& \overline{\beta(U)}
},$$
 where $\overline{C}$ is smooth, since it is normal and of dimension one. Let $C$ be the image of the map $f|_U$. Then we have the following commutative diagram:
 $$ \xymatrix{
U \ar[r]^{f|_U} \ar[d] & C \ar[r] \ar[d] & \beta(U) \ar@{^{(}->}[d] \\ 
\Alb(U) \ar[r] & \Alb(C) \ar[r] & T }
 $$
Notice that the the holomorphic 1-form $dz_1$ over $T$ which pulls back to logarithmic 1-form $\omega$. Therefore to finish the proof, it suffices to show that $T$ is indeed isomorphic to $\Alb(C)$. 
Note that since $f|_U:U\to C$ is surjective and has connected fibers, the induced map on the first homology groups $H_1(U,\Z) \to H_1(C,\Z)$ is surjective{\color{red}(Check!!!)}. It implies that $\Alb(U) \to \Alb(C)$ is surjective. Now it is clear that all the horizontal maps in the diagram are surjective. 
%Then we have the following commutative diagram:
%$$\xymatrix{
%\overline{C} \ar[rd] \ar[r]^f & \overline{\beta (U)} \ar[d]  \\
%\Alb(\overline{C})& A(T)
%}$$
Since $\beta(E)$ is a point in $T$, so $E$ maps to a point in $\beta(U)$. Thus $E$ maps to a point in $C$. Up to choosing a base point, we get that $ T_0$ is contained in the kernel of $A_U \to A_C$, since $\alpha_U(E)=T_0$. Hence $A_C=T$, i.e., $T$ is the Albanese variety of $C$


%Hence $C$ cannot be $\mathbb{P}^1$ or $\mathbb{C}$ and the Albanese map of $C$ is injective. In fact, for positive genus case, this follows from the fact that the Albanese map of a positive genus smooth projective curve is an embedding; while for zero genus case, this is obvious. The case where $C$ being isomorphic to $\C$ is impossible as its image in $T$ has to be just one point.

%Then  $A_C=T$ implies $C$ is isomprhic to $\beta(U)$. Hence $\beta(U)$ and $\overline{\beta(U)}$ are both smooth.

%Again, $\overline{U}$ could be different from $X$. But $H^0(\overline{U},\Omega_{\overline{U}}^1(\log (\overline{U}-U)) )=H^0(X, \Omega_X^1(\log D))$. Then we are done.} 
The higher dimensional case follows immediately from Lefschetz hyperplane theorem. (TBA more details)
\end{proof}

\begin{theorem}\label{thm:Spurr-quasi-proj}
Let $(X, D)$ be a pair with $X$ a complex smooth projective variety and $D$ a simple normal crossing divisor of $X$. Let $H$ be an ample divisor on $X$. Suppose $(X, D)$ carries a nontrivial logarithmic 1-form $\omega\in H^0(X, \Omega_X^1(\log D))$  which restricts to zero on an integral divisor $E$ with $E^2\cdot H^{n-2}\geq0$, then there is a surjective morphism $f: X-D\to C$ to a smooth quasi-projective curve $C=\bar{C}-B$ ($B$ can be empty) with 

(1)  $\omega=f^*\eta$ for some $\eta\in H^0(C, \Omega_C^1(\log B))$.

(2) $f$ has connected fibers.

(3) $E$ is contained in the fiber of $f$ and $E^2\cdot H^{n-2}=0$.
\end{theorem}

\begin{proof} With out losing of generality, we may assume that $D=\sum_{i=1}^s D_i$ and $E$ intersects each component of $\{D_1, \ldots, D_t\}_{t\leq s}$ nontrivially and does not intersect other components $D':=\sum_{i=t+1}^sD_i$.
Consider the following commutative diagram of short exact sequences
$$
\xymatrix{
 0\ar[r]&\Omega_X^1(\log D')\otimes\mathcal{O}_X(-E) \ar[r]\ar[d]& \Omega_X^1(\log D')\ar[r]\ar[d] & \Omega_X^1(\log D')|_{E} \ar[d] \ar[r]&0\\
   0\ar[r]& \Omega_X^1(\log D)\otimes\mathcal{O}_X(-E)\ar[r]& \Omega_X^1(\log D) \ar[r]& \Omega_X^1(\log D)|_{E}\ar[r] &0
.  }
$$Then it induces the following commutative diagram of exact sequences
$$\label{holo-log-form-compare}
\xymatrix{
 H^0(X, \Omega_X^1(\log D')\otimes\mathcal{O}_X(-E)) \ar[r]\ar[d]& H^0(X, \Omega_X^1(\log D'))\ar[r]\ar[d] & H^0(\Omega_X^1(\log D')|_{E}) \ar[d] \\
   H^0(X, \Omega_X^1(\log D)\otimes\mathcal{O}_X(-E))\ar[r]& H^0(X, \Omega_X^1(\log D)) \ar[r]& H^0(X, \Omega_X^1(\log D)|_{E})
.  }
$$

Firstly, we want to show the left vertical arrow is an isomorphism under the assumption that $E$ intersects each component of $\{D_i\}_{i=1}^t$ nontrivially. Now consider the short exact sequence $$0\to\Omega_X^1(\log D')\to \Omega_X^1(log D)\to \nu_*\mathcal{O}_{\widetilde{D}}\to 0,$$ where $\widetilde{D}$ is a disjoint union of $D_1, \ldots, D_t$ and  $\nu: \widetilde{D}\to X$ is the natural map. Then we get the short exact sequence $$0\to\Omega_X^1(\log D')\otimes\mathcal{O}_X(-E)\to \Omega_X^1(log D)\otimes\mathcal{O}_X(-E)\to \nu_*\mathcal{O}_{\widetilde{D}}\otimes\mathcal{O}_X(-E)\to 0.$$ Thus to show left vertical arrow in diagram (\ref{holo-log-form-compare}) is an isomorphism, we just need to show that $$H^0(X, \nu_*\mathcal{O}_{\widetilde{D}}\otimes\mathcal{O}_X(-E))=0.$$ In fact, $$H^0(X, \nu_*\mathcal{O}_{\widetilde{D}}\otimes\mathcal{O}_X(-E))=H^0(\widetilde{D}, \nu^*\mathcal{O}_X(-E)).$$ Since $E$ intersects each component of $\{D_1, \ldots, D_t\}_{t\leq s}$ nontrivially, $\nu^*\mathcal{O}_X(E)=\nu^*\mathcal{O}_X(-E)^{\vee}$ is a nontrivial effective line bundle over each connected component of $\widetilde{D}$. Hence we get $H^0(\widetilde{D}, \nu^*\mathcal{O}_X(-E))=0$. 

Then by chasing in diagram (\ref{holo-log-form-compare}), the logarithmic 1-form $$\omega\in H^0(X, \Omega_X^1(\log D')).$$ Since $D'\cap E=\emptyset$ and $H^0(X, \Omega_X^1(\log D'))\subset H^0(X, \Omega_X^1(\log D))$, the whole theorem follows from Proposition \ref{Prop:Spurr-no-intersection}.
\end{proof}

\begin{proof}[Proof of Theorem \ref{thm:codim1quasiprojective}]

The theorem follows immediately from Theorem \ref{thm:Spurr-quasi-proj}.
\end{proof}

































\begin{thebibliography}{HKLR} 


%\bibitem[AMN]{AMN} J. Amor\'os, M. Manjar\'in,  M. Nicolau, \textit{Deformations of K\"ahler manifolds with nonvanishing holomorphic vector fields}, J. Eur. Math. Soc. \textbf{14}, (2012), 997--1040.


%\bibitem[BeFa08]{BeFa08} K. Behrend, B. Fantechi,  \textit{Symmetric obstruction theories and Hilbert schemes of points on threefolds},  Algebra and Number Theory,  \textbf{2} (2008), 313--345.

\bibitem[Ara92]{Ara92} D.\ Arapura, ``Higgs line bundles, Green-Lazarsfeld sets, and maps of K\"ahler manifolds to curves", \textit{Bull., New Ser.,
Am. Math. Soc.}, vol.\ \textbf{26} (1992), pp.\ 310--314.

\bibitem[Ara97]{Ara97} D.\ Arapura, ``Geometry of cohomology support loci for local systems, I". \textit{Journal of Algebraic Geometry} vol.\ \textbf{3} (1997): pp.\ 563--597.


\bibitem[BWY16]{BWY16} N. Budur, B. Wang, Y. Yoon, \textit{Rank one local systems and forms of degree one}. Int. Math. Res. Not. \textbf{13} (2016), 3849--3855.



\bibitem[CL73]{CL73} J. B. Carrell, D. I. Lieberman,  \textit{Holomorphic vector fields and K\"ahler manifolds}, Invent. Math. \textbf{21} (1973), 303--309.

\bibitem[Deb07]{Deb} O. Debarre,  \textit{On the geometry of abelian varieties} \url{https://www.math.ens.fr/\textasciitilde debarre/Taiwan.pdf}, (2007).

\bibitem[DJL17]{DJL17} O.\ Debarre, Z.\ Jiang and M.\ Lahoz, Rational cohomology tori, \textit{Geometry \& Topology} vol.\ 21 (2017),
pp.\ 1095--1130.

\bibitem[DiPa13]{DiPa13}A. Dimca, S. Papadima, \textit{Nonabelian cohomology jump loci from ananalytic view point}. Commun. Contem. Math. \textbf{15} (5), 1350025 (2013).


\bibitem[DiSu]{disu} A. Dimca, A. I. Suciu, \textit{Which 3-manifold groups are K\"ahler groups?}, J. Eur. Math. Soc., \textbf{11} (2009), no. 3, 521-528.

\bibitem[GH18]{GH18} I. Glazer, Y. I. Hendel, \textit{On singularity properties of convolutions of algebraic morphisms--the general case (with an appendix joint with Gady Kozma)}, arXiv:1811.09838.

\bibitem[GH19]{GH19}  I. Glazer, Y.I. Hendel, \textit{On singularity properties of convolutions of algebraic morphisms}, Selecta Mathematica (2019), pp.\ 25--15


\bibitem[GL87]{GL87} M. Green, R. Lazarsfeld, \textit{Deformation theory, generic vanishing theorems and some conjectures of Enriques, Catanese and Beauville}, Inv. Math. \textbf{90} (1987), 389--407.

\bibitem[GW10]{GW10} U. G\"ortz, T. Wedhorn, \textit{Algebraic geometry I. Schemes with examples and exercises.} Advanced Lectures in Mathematics. Vieweg+Teubner, Wiesbaden, 2010. 

\bibitem[HK05]{HK05} C. D. Hacon, S. J. Kov\'acs, \textit{Holomorphic one-forms on varieties of general type}, Ann. Sci. \'Ecole Norm. Sup. \textbf{38} (2005), no. 4, 599--607.

\bibitem[Har77]{Har77} R. Hartshorne, \textit{Algebraic Geometry}, Graduate Texts in Mathematics, vol. 52, Springer, New York,
1977.

\bibitem[HS19]{HS19} F. Hao, S. Schreieder, \textit{Holomorphic one-forms without zeros on threefolds}, to appear Geometry $\&$ Topology , arXiv:1906.07606.

\bibitem[KK]{KK} J. Koll\'ar, S. Kov\'acs {\it Singularities of the Minimal Model Program.}
Series: Cambridge Tracts in Mathematics (No. 200)

\bibitem[Laz04a]{Laz04a}
    R. Lazarsfeld. \textit{Positivity in algebraic geometry.\ I.\ Classical
    setting: line bundles and linear series}.
    Ergeb.\ Math.\ Grenzgeb.\ (3), Vol.\ 48. Berlin: Springer-Verlag, 2004.
    \textsc{doi}: \href{https://doi.org/10.1007/978-3-642-18808-4}{\ttfamily 10.1007/978-3-642-18808-4}.
    \textsc{mr}: \href{http://www.ams.org/mathscinet-getitem?mr=2095471}{\ttfamily 2095471}.


\bibitem[Laz04b]{Laz04}
    R. Lazarsfeld. \textit{Positivity in algebraic geometry.\ II.\ Positivity
    for vector bundles, and multiplier ideals}.
    Ergeb.\ Math.\ Grenzgeb.\ (3), Vol.\ 49. Berlin: Springer-Verlag, 2004.
    \textsc{doi}: \href{https://doi.org/10.1007/978-3-642-18810-7}{\ttfamily 10.1007/978-3-642-18810-7}.
    \textsc{mr}: \href{http://www.ams.org/mathscinet-getitem?mr=2095472}{\ttfamily 2095472}.

%\bibitem[KM05]{KM05} J. Koll\'ar and S. Mori, \textit{Birational geometry of algebraic varieties}, Cambridge University Press, Cambridge, 2008.

%\bibitem[Mo85]{Mo85} S. MORI S, \textit{Classification of higher-dimensional varieties}, in: Algebraic Geometry, Bowdoin, (1985),Brunswick, Maine, (1985), in: Proc. Sympos. Pure Math., \textbf{46}, American Mathematical Society,Providence, RI, (1987), 269--331.

%\bibitem[LMW18]{LMW18} Y. Liu, L. Maxim, B. Wang, {\it Perverse sheaves on semi-abelian varieties}, arXiv: 1804.05014. 

\bibitem[LMW20]{LMW20} Y. Liu, L. Maxim, B. Wang, \textit{Aspherical manifolds, Mellin transformation and a question of Bobadilla-Koll\'ar}, arXiv:2006.09295.

\bibitem[LZ05]{LZ05} T.\ Luo and Q.\ Zhang, Holomorphic forms on threefolds, \textit{Recent Progress in Arithmetic and Algebraic Geometry, Contemp.\ Math, Amer.\ Math.\ Soc.}, vol.\ 386, pp.\ 87--94 Providence, RI, (2005). 
\textsc{doi}: \href{https://doi.org/org/10.1090/conm/386/07219}{\ttfamily 10.1090/conm/386/07219}.
\textsc{mr}: \href{http://www.ams.org/mathscinet-getitem?mr=2182772}{\ttfamily 2182772}.

\bibitem[MiSh18]{MiSh18} L. Migliorini and V. Shende, \textit{Higher discriminants and the topology of algebraic maps}, Algebraic geometry, (2018), 114--130.

\bibitem[Mum]{Mum} D. Mumford, \text{Abelian Varieties}, Tata Institute of Fundamental Research, (1985).

\bibitem[PS14]{PS14} M. Popa and C. Schnell, \textit{Kodaira dimension and zeros of holomorphic one-forms}, Ann. of Math. \textbf{179} (2014), 1109--1120.


\bibitem[Sha74]{Sha74} I. Shafarevich, \textit{Basic Algebraic Geometry I}. Berlin, Springer--Verlag, (1974).

\bibitem[Sch15]{Sch}
C. Schnell, {\it  Holonomic $\mathcal{D}$-modules on abelian varieties},
Publ. Math. Inst. Hautes \'{E}tudes Sci. 121 (2015), 1--55.

\bibitem[Sch19]{SS19} S.\ Schreieder, \textit{Zeros of holomorphic one-forms and topology of K\"ahler manifolds, (Appendix written jointly with H.-Y. Lin) }, to appear IMRN. (2019).

\bibitem[Schm76]{Schm76} W. Schmid, Variation of Hodge structure: the singularities of the period mapping, Inv. Math. \textbf{22} (1973), 211--319.

\bibitem[Ste76]{Ste76} J. Steenbrink, \textit{Limits of Hodge structures}, Inv. Math. \textbf{31} (1976), 229--257.




\bibitem[Sim93a]{Sim93} C. Simpson, \textit{Lefschetz theorems for the integral leaves of a holomorphic one-form}, Compositio Math. \textbf{87} (1993), 99--113.

\bibitem[Sim93b]{Sim93b} ---------, Subspaces of moduli spaces of rank one local systems, \textit{Ann. Sci. \'Ec. Norm. Super.}, vol.\ 26,
pp.\ 361-401 (1993).

\bibitem[Sp88]{Sp88} M. Spurr, {\it On the zero set of a holomorphic one-form on a compact complex manifold.} Trans. Am.
Soc. \textbf{308} (1988), 329-339. 

\bibitem[stacks-project]{stacks-project} The {Stacks project authors}, \textit{The Stacks project}, \url{https://stacks.math.columbia.edu}, (2020).

\bibitem[Uen75]{Uen75} K.\ Ueno. ``Classification theory of algebraic varieties and compact complex spaces", \textit{Lecture Notes in Mathematics},
Springer-Verlag, Berlin, 1975, Notes written in collaboration with P. Cherenack, Vol.\ \textbf{439}. 
\textsc{mr}: \href{http://www.ams.org/mathscinet-getitem?mr=0506253}{\ttfamily 0506253}.


\end{thebibliography}

\end{document}